SPARQL on the Open, Decentralised Web

### 2016-07-25 dissertation/problems.tex
more explanations in problems #6

@@

@@

\begin{problem}\label{prob:queryeq}
Determining that two queries will return the exact same answer is a
complex problem.
\end{problem}

\begin{problem}\label{prob:sanity}
It is not known how much of the Semantic Web exposes information that
could be used in HTTP caching.
\end{problem}

\begin{problem}\label{prob:nostats}
A caching proxy far removed from the database it caches may have
little or no statistics for query optimisation.
\end{problem}

>>>>

Even if this statistics could be found, it is not clear that it should:
\begin{problem}\label{prob:largestats}
Comprehensive statistics may be costly to compute and requires much
storage space.
\end{problem}
Therefore, it is important to find a balance.

@@

The performance issue discussed in Section~\ref{sec:prelimquery} has
relevance in the context of caching:

@@

To understand this, consider Example~\ref{ex:cartesian}, where the BGP
was a part of a query with 3 triple patterns. In addition to the two
triple patterns in Example~\ref{ex:cartesian}, a triple pattern that
connected the two, for example
\rdfterm{?person~foaf:publications~?paper~.}. If the result of this
triple pattern is cached, what is left to evaluate are the two triple
patterns in Example~\ref{ex:cartesian}, which is likely a very
expensive operation.

It would be useful when caching if one could compare the incoming
query to a query with an already cached result and determine that they
were equivalent, but unfortunately:
\begin{problem}\label{prob:queryeq}
Determining that two queries will return the exact same answer is a
complex problem.
\end{problem}

Metadata is important for query planning, and as explained in
Section~\ref{sec:httpcache}, the HTTP protocol provides facilities for
sharing such information. However:
\begin{problem}\label{prob:sanity}
It is not known how much of the Semantic Web exposes information that
could be used in HTTP caching.
\end{problem}

Even though statistics may be available internally in a query engine,
a caching proxy is unlikely to have direct access to that data, and therefore:
\begin{problem}\label{prob:nostats}
A caching proxy far removed from the database it caches may have
little or no statistics for query optimisation.
\end{problem}
